\begin{document} \newline \title{Treacherous Blaze} \newline \author{G. U. Cook} \newline \newline \maketitle \par \par \chapter{Front Matter} \par  For a limited time only, this title is just \$0.99! Get it before the deal is over! Janine is happy single, but her best friend Ischara. Ischara has insisted time and time again -- just meet this one guy, and your life will be amazing. Finally, Janine agreed -- and now she finds herself face to face with a brand new person, Franklin. Franklin is a calm, handsome young professional desperate to find someone to fall in love with. Will Janine and Franklin find love? Or will their fears keep them from fulfilling their needs? Join Janine and Franklin as they explore each others' bodies for the first time. We are Tales For Cash, an indie publishing firm, and we want your stories and novels! Receive a lump sum for your initial accepted manuscript, and a percentage of royalties when your book begins to make a profit! Check us out at TalesForCash.com today to get started! With a minimum of 2,500 words, it's easy for you to publish quickly and get paid soon. Why sit and wait for word-of-mouth to sell your book? Get started today! \par \chapter{Chapter 1} \par  What if this day was different? What if Janine could date someone decent instead of another destroyed brute? Honestly, love couldn't be that immense. \par Janine mused while Janine grabbed for her phone. Despite the many abrasion, the blue leather was silken in her hands. She was able to excel at it. Janine ached to do this. She had desires, and aspirations, and she was prepared to start fresh. \par The oven clock caught her eye, green digits staring at at her. 2:34. Janine was already incredibly late. \par ``Aw, fuck!'' Groaning, she stood. It was time. She stared towards the door, getting up. ``Don't be naughty, right, Kaleb?'' She glowered at her cat, laying on the nightstand with a kind look on his sweet face.  She stroked her orange tabby cat, who was roosted on the coffee table. ``No destroying the kitchen again. I don't want to clean up a mess.'' \par She strode towards the cat and stretched to scratch his butt, but he flashed off towards the kitchen instead. Janine shook her head. She headed out the door. \par \par \chapter{Chapter 2} \par  It only took a couple of minutes to get there. The celestial fireball in the sky was intense, and harsh. Janine found the radio rather irritating, and briefly shut it down, preferring quiet to stop her heaving stomach. Why couldn't her nerves calm down? \par The bar was a simple place, vivid and embracing. She felt her heart pounding in her chest as she wondered what rested beyond the opening. \par ``Janine, over here!'' Janine thought she heard Ischara. she looked through the vivid sun to see Ischara and her well-worn GMC. \par ``Hey there, Ischara.'' Janine responded. ``Is he here yet?'' They hugged. \par ``Not sure. He contacted me just a few moments ago to say he was nearly here.'' Ischara stared at her phone, stroking its glass lightly. ``He hasn't answered me back.'' ``she gazed towards the bar. He might be inside.'' \par Ischara had set up the meeting, and it was essentially a blind date, with one small exception. Ischara had vowed to introduce them, to avoid that whole seeking blindly and awkward meeting thing that usually went on. \par He was attractive. Mussed auburn mane, a little bit of stubble, and piercing eyes. Never mind his hot grin. He was too good to be true. \par ``How is this man single, again?'' Janine asked conversationally as they entered through the wooden opening. \par ``There's nothing wrong with this one.'' Ischara mused. ``There's nothing wrong with any of them. It is \textit{you}, my dear, who is so damned picky.'' Ischara looked around for he. \par ``Hm.'' She declared. ``I see him.'' Ischara gestured to the silhouette of a man in the corner. \par ``You think so?'' Ischara nodded, grinning. ``Yeah. He loves that damn tee. It's his favorite.'' \par Bright pink and way too small, his shirt was telling. she could see the definition below the t-shirt. \par ``Wow. He's hot.'' Janine said. Thankfully, he couldn't hear them. \par ``Come on.'' They headed towards his table. \par ``Hey, Franklin!'' Ischara touched his shoulder, and he jumped and turned. He smiled. \par ``Ischara, how are you!'' He got up to say hello. Janine sat down. \par ``Well, friends, I don't like to be the debbie-downer, but my end of the deal is done. Janine? Don't be naughty. Franklin? You be good. I'll catch you friends later.'' \par They watched Ischara go. It was time. \par \chapter{Chapter 3} \par  ``So, this is otherworldly.'' Franklin said, peering at the menu. ''I don't think I've ever done this before.'' He glanced at Janine. ``And I'm kinda nervous.'' \par ``Ischara hasn't tried to set you up with someone before?'' Janine was fixated on just how kissable he was. He was a sexy, attractive man, and the photo she had seen might not do him justice. She wondered if he could see into her soul. \par ``Is this a regular thing for you?'' He asked, eyebrows raised. She shook her head and winked. \par ``Only once or twice before. Ischara has this thing about single friends. She's doing what she thinks is best.'' \par ``She means well.'' Franklin said. ``I think she chose well.'' She felt her insides tingle. \par ``Wow, thanks!'' She grinned. She could feel her fingertips tingle, her stomach ached. \par ``So, where are you from?'' Franklin said. ``Tell me everything.'' \par ``My entire life?'' She snortled. ``That'll take forever. How about the abridged version? I was born in Wyoming, New York, and I wandered for a while before settling here. How about yourself?'' \par ``I wish I was interesting. I grew up in Union City and moved here for work.'' \par ``That's cool.'' She brushed her hair from her face and snickered. His fingers were meticulously trimmed and touching ever so quietly on the menu, an unconscious tic that was oddly endearing. ``What do you do?'' \par ``Hi friends, I'm Elsa...'' The waitress surprised her. ``Can I get you girls anything to drink?'' \par ``How about a Angry Orchard?'' Franklin asked, noting the confused look on Janine's face. Franklin grinned, turning to Janine. \par ``A Pepsi, please.'' Janine frowned. ``Thanks.'' \par ``Great! I'll be right back.'' She left them in silence. \par ``What were we talking about?'' \par ``Careers.'' Franklin smiled. ``And I'm an IT consultant, so that's about as boring as you can get right? I work with Ischara.'' \par ``That's cool. Perfectly predictable.'' she snorted. ``I wish I had a secure job. I write for magazines. There are tons of freelances who don't get paid, and they,'' she mused, ``they make my position very expendable.'' \par Franklin looked at her sorrowfully. ``Yeah, the market sucks for that kind of thing. I actually wanted to be a writer for a long time, but it never really panned out.'' \par ``It's a rough life, don't bother.'' Janine grumbled, and Franklin chuckled. \par ``That's true! I could take your cushy position.'' He stroked her hand. ``Ischara talked you up like you were the best thing since sliced bread. I'm starting to see why she loves you.'' He released her finger. Janine's hand was tingling. His eyes pierced her soul. ``You are so dynamic. Why haven't you settled down yet?'' \par ``I thought we weren't doing that question?'' Janine chuckled nervously. He winked. \par ``I know, I know. But still, tell me. Who are you waiting for? What was your longest relationship? Why did you break up?'' \par ``Just one.'' She responded, finding her courage again. A hammer pounded in her chest. ``He and I... I loved him so hard. I just couldn't take his excuses. I drew the line when I found him taking dick-pics in my bathroom to send to one of his other girlfriends.'' \par Franklin winced. ``Ouch. I've never been in love. I wasn't ready. I get lonely now, and beer doesn't taste as good. I want something my parents never could have, with their serial divorces. I want to find my future wife. Someone to raise my children -- if I even want children. I just need some meaning in my life.'' \par Janine's heart melted. So there was a decent friend out there. Where had Franklin been all of her life? \par Glasses clinked together, distracting her. ``Here are your drinks. Any food?'' \par \chapter{Chapter 4} \par  ``I had a great time today.'' She winked up at him. ``I certainly didn't start the day thinking that we'd be together all day.'' \par ``I really enjoyed myself.'' Janine winked. She hadn't quite shaken the sense of surrealism that had started earlier, at the bar. Her stomach raged with anticipation. ``Come inside.'' \par ``I don't know...'' he commented. ``I don't want to mess whatever this is up. Won't Ischara kill us?'' \par ``Ischara can go fuck herself.'' Janine pushed her fears aside and leaned into him, staring into his eyes. He knew what she wanted, and leaned down to kiss her. The fire that had been building all day angered inside Janine as his luxurious, warm lips pressed against hers. Her nipples hardened underneath her t-shirt, and her pulse quickened, warmth spreading through her belly and farther south. \par They kissed forever, until he finally stepped back. ``Alright. I'm in.'' \par Janine fumbled with her keys for a moment or two before finding the right one. Successful, she opened the door and motioned. ``It's not much.'' She said, dropping her hand-bag on the coffee table. Kaleb was near the door. ``Oops. It's past his dinner time.'' \par ``So that's what Ischara was hiding.'' He said with a smile. ``How many little beasts do you have?'' \par ``Just one cat. This is my life partner, Kaleb.'' Janine stroked Kaleb. She felt the tension rise. ``Sorry, he can be a dick when he's hungry. He's probably starving.'' \par ``I get it. Not a problem.'' He watched her walk towards the kitchen. \par ``Please, make yourself at home.'' She said. ``I'll be right in.'' He surveyed the small, but classy living room. Franklin took a seat on her couch. \par ``I like this couch.'' Franklin winked. \par ``I can't bear to let it go.'' She stood in the light of the kitchen, watching him. ``First furniture I ever bought new.'' \par ``I see.'' Franklin grabbed her hand, seating her on his lap. ``And now, us.'' He stroked her cheek. ``Am I going too fast?'' He smiled at her. He watched as she shook her head. ``Okay then.'' He kissed her again, fire racing through her belly. Janine wondered if he was as excited as she was. \end{document}
